---
title: "Lab_10"
author: "Data Me Pls: Chris, James, Amanda, Anna"
date: "March 17, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# IT'S ALMOST SPRING BREAK (AND I'M READY TO GIVE 0% EFFORT ON THIS LAB)
```{r, eval= FALSE}
# Load Both Parts of this Data
library(tidyverse)
library(lubridate)
answers <- read_csv("Answers_trunc.csv", col_names = TRUE)%>%
  select (Id, OwnerUserId, CreationDate, ParentId, Score, Body)
View(answers)

questions <- read_csv("Questions_trunc.csv", col_name= TRUE)%>%
  select(Id, OwnerUserId, CreationDate, Score, Title, Body)
View(questions)

## Join if you want (run all code)
answersj <- answers%>%
  rename(AnswerId= Id, Id= ParentId)

QnA <- full_join(questions, answersj, by= "Id")%>%
  rename(QDate= CreationDate.x,
         QScore= Score.x,
         QTitle= Title,
         QBody= Body.x,
         ADate= CreationDate.y,
         AScore= Score.y,
         ABody= Body.y,
         AUserId= OwnerUserId.y,
         QUserId= OwnerUserId.x,
         Aid= AnswerId,
         Qid= Id
         )
  
QnA <- QnA%>%
  select(Qid, QTitle, QDate, QScore, QUserId, QBody, 
         Aid, ADate, AScore, AUserId, ABody)
```

## Timeliness of a Post (GROUP)
```{r, eval=FALSE}
time <- QnA%>%
  select(Qid, QDate, ADate, AScore)

etime <- time%>%
  mutate(Etime= ADate-QDate)

### DATA LOSS HERE
etime1 <- etime%>% 
  filter(Etime >= 0)

ggplot(etime1)+
  geom_point(mapping= aes(x=Etime, y=AScore))

```

## Other Important Features (SUMMARY OF INDIVIDAL)

---

### Chris

### James

### Amanda 
__Questions:__ Do questions that include a question mark generally receive more upvotes than questions that do not include a question mark?

```{r, eval=FALSE}
questions %>% mutate()
```



__Answers:__ Do answers that use "I statements get more upvotes than ones that don't?"

```{r, eval=FALSE}

```

### Anna (If answers were higher voted than question)
Feature: Your Question Sucks!

```{r, eval=FALSE}
updoot <- QnA%>%
  mutate(Diff= AScore-QScore)

updoot1 <- updoot%>%
  filter(Diff > 0)

ggplot (updoot1)+
  geom_point(mapping=aes(x=Diff, y=QScore, color=AScore))

```