---
title: "Lab 7"
author: "Data Me Pls: Chris, James, Amanda, Anna"
date: "February 22, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
library(tidyverse)
<<<<<<< HEAD

household_power_consumption <- read.csv("~/Downloads/household_power_consumption.txt", header=FALSE, sep=";")housepwr <- read.delim2(unz("household_power_consumption.zip", "household_power_consumption.txt"),
                        sep= ";", header= FALSE)
=======
install.packages("data.table")
library(data.table)
housepwr <- read.delim(unz("household_power_consumption.zip", "household_power_consumption.txt"),
                       sep= ";", 
                       header= TRUE, 
                       na.strings= c("NA","","?"), 
                       stringsAsFactors= FALSE)

housemon <- housepwr %>%
  separate(Date, into= c("day","month","year"), sep= "/", convert= TRUE)
>>>>>>> master
```

# Findings

# Dataset Description

---
<<<<<<< HEAD

## Amanda

```
householdPowerConsumption <- read.table("~/Downloads/household_power_consumption.txt", header=T, na.strings=c("NA", "", "?"), sep=";", stringsAsFactors = FALSE)

householdPwr <- householdPowerConsumption %>% separate(Date, into=c("Day", "Month", "Year"), sep = "/", convert = TRUE)
View(householdPwr)

```


       


=======
  
## Amanda (month, submetering 1)
How does energy consumption in the kitchen change across months?
How does the proportion of each type of energy consumption change across months?
>>>>>>> master


-graph
-summary statistic
  
## James
  
## Chris (global, month)
How does average global active power change every month throughout the four years? 
  
## Anna (month, submetering 3)

