<<<<<<< HEAD
---
title: "Lab 13"
author: "Data Me Pls: Amanda, James, Chris, Anna"
date: "April 12, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
library(tidyverse)
library(gapminder)
gapminder <- gapminder

#Run this code to get the new data
library(readxl)
Indicator_HDI <- read_excel("Indicator_HDI.xlsx")

Indicator_HDI2 <- Indicator_HDI%>%
  na.omit()

Indicator_HDI3 <- gather(Indicator_HDI2, key="year", values=
         `1980`,`1990`,`2000`,`2005`,`2006`,`2007`,`2008`,`2009`,`2011`)

names(Indicator_HDI3) <- c("country", "year", "HDI")

Indicator_HDI3 <- transform(Indicator_HDI3, year=as.numeric(year))

gapminder2 <- full_join(Indicator_HDI3, gapminder, by= c("country", "year"))

gapminder3 <- gapminder2%>%
  na.omit()
view(gapminder3)

#This entire dataset only has the year 2007 as it was the only year both gapminder and the hdi were recorded. We will all compare two continent groupings (e.g. Asia and America) to see if there is a significant difference between the histogram and the true data.

```

## Amanda

__Question:__ Is there a significant difference between the mean Human Development Index in the United States and Canada versus the mean HDI for the world?

```{r, Eval=FALSE}
hdi <- gapminder3 %>% select(HDI)
hdi <- hdi$HDI
#view(hdi)

perm_mean <- function(perms = 1000, values, n1)
{
  # Create vector of zeroes of length "perms" to store permuted mean differnces
  mean_mat <- matrix(0,1000,1)
  # Loop throught number of permutations
  for (i in c(1:perms))
  {
    randomSamp <- sample(values, length(values)-n1, replace = FALSE)
    randomSamp2 <- sample(values, n1, replace = FALSE)
    # Compute the sample means for the two groups from step 2
    mean1 <- mean(randomSamp)
    mean2 <- mean(randomSamp2)
    # Compute the difference in sample means, store the value in the vector from step 1
    mean_mat[[i]] <- (mean1-mean2)
  }
  # Return new updated vector, created in step 1
  return(mean_mat)
}
hdiAmerica <- gapminder3 %>% filter(country=="Canada" | country=="United States") %>% select(HDI)
means <- as.tibble(perm_mean(values = hdi, n1 = 2))
summary(hdiAmerica)
summary(hdi)
#view(hdiAmerica)

realDiff <- mean(hdiAmerica$HDI)-mean(hdi)

stdD <- sqrt((sd(hdiAmerica$HDI))^2/length(hdiAmerica$HDI) + (sd(hdi))^2/length(hdi))
zScore <- realDiff/stdD
zScore
# zScore = 1.793
ggplot(means, aes(x=V1 ))+geom_histogram()+
  xlab("Means")+
  geom_vline(xintercept = realDiff, color = "blue", size = .3)+
  ylab("Number")+
  ggtitle("Difference in Means of Life Expectancy")
```

## James

## Chris

## Anna

__Question:__ Is there a correlation between 
```{r, Eval=FALSE}
gapminder4 <- gapminder3%>%
  filter(continent== "Asia"| continent== "America")

hdi <- gapminder4%>%
  select(HDI)

life_exp <- gapminder4%>%
  select(lifeExp)

life_exp <- life_exp$lifeExp
pop_size <- pop_size$pop

real_cor <- cor(pop_size,life_exp)

perm_cor <- function(perms = 1000, x, y)
{
  corr_mat <- matrix(0,length(perms),1)
  mylist <- rep(list(0,1000))

  for (i in c(1:perms))
  {
    mylist[[i]] <- sample(y, length(y), replace = FALSE)
    corr_mat[[i]] = real_cor + cor(x,mylist[[i]])
  }
  return(corr_mat)
}

correlation <- as.tibble(perm_cor(x=life_exp,y=pop_size))

props <- as.tibble(quantile(perm_cor(x=pop_size,y=life_exp)))

standard_dev <- sd(perm_cor(x=life_exp,y=pop_size))

summary(correlation)


ggplot(correlation, aes(x=value))+geom_histogram() + labs(x= "correlation", y = "count", title = "correlation between GDP per capita and life expectency")+ geom_vline(xintercept = real_cor, col = "Blue")
```
=======
---
title: "Lab 13"
author: "Data Me Pls: Amanda, James, Chris, Anna"
date: "April 12, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
library(tidyverse)
library(gapminder)
gapminder <- gapminder

#Run this code to get the new data
library(readxl)
Indicator_HDI <- read_excel("Indicator_HDI.xlsx")

Indicator_HDI2 <- Indicator_HDI%>%
  na.omit()

Indicator_HDI3 <- gather(Indicator_HDI2, key="year", values=
         `1980`,`1990`,`2000`,`2005`,`2006`,`2007`,`2008`,`2009`,`2011`)

names(Indicator_HDI3) <- c("country", "year", "HDI")

Indicator_HDI3 <- transform(Indicator_HDI3, year=as.numeric(year))

gapminder2 <- full_join(Indicator_HDI3, gapminder, by= c("country", "year"))

gapminder3 <- gapminder2%>%
  na.omit()
view(gapminder3)

#This entire dataset only has the year 2007 as it was the only year both gapminder and the hdi were recorded. We will all compare two continent groupings (e.g. Asia and America) to see if there is a significant difference between the histogram and the true data.

```

## Amanda

__Question:__ Is there a significant difference between the mean Human Development Index in American countries versus the mean HDI for the world?

```{r, Eval=FALSE}
hdi <- gapminder3 %>% select(HDI)
hdi <- hdi$HDI
#view(hdi)

perm_mean <- function(perms = 1000, values, n1)
{
  # Create vector of zeroes of length "perms" to store permuted mean differnces
  mean_mat <- matrix(0,1000,1)
  # Loop throught number of permutations
  for (i in c(1:perms))
  {
    randomSamp <- sample(values, length(values)-n1, replace = FALSE)
    randomSamp2 <- sample(values, n1, replace = FALSE)
    # Compute the sample means for the two groups from step 2
    mean1 <- mean(randomSamp)
    mean2 <- mean(randomSamp2)
    # Compute the difference in sample means, store the value in the vector from step 1
    mean_mat[[i]] <- (mean1-mean2)
  }
  # Return new updated vector, created in step 1
  return(mean_mat)
}
hdiAmerica <- gapminder3 %>% filter(continent=="Americas") %>% select(HDI)
means <- as.tibble(perm_mean(values = hdi, n1 = 23))
summary(hdiAmerica)
summary(hdi)
#view(hdiAmerica)

realDiff <- mean(hdiAmerica$HDI)-mean(hdi)

stdD <- sqrt((sd(hdiAmerica$HDI))^2/length(hdiAmerica$HDI) + (sd(hdi))^2/length(hdi))
zScore <- realDiff/stdD
zScore
# zScore = 1.793
ggplot(means, aes(x=V1 ))+geom_histogram()+
  xlab("Means")+
  geom_vline(xintercept = realDiff, color = "blue", size = .3)+
  ylab("Number")+
  ggtitle("Difference in Means of Life Expectancy")
```

## James

## Chris

## Anna

__Question:__ Is there a correlation between HDI and Life Expectancy
```{r, Eval=FALSE}
hdi <- gapminder3%>%
  select(HDI)

life_exp <- gapminder3%>%
  select(lifeExp)

life_exp <- life_exp$lifeExp
hdi <- hdi$HDI

real_cor <- cor(hdi,life_exp)

perm_cor <- function(perms = 1000, x, y)
{
  corr_mat <- matrix(0,length(perms),1)
  mylist <- rep(list(0,1000))
  
  for (i in c(1:perms))
  {
    mylist[[i]] <- sample(y, length(y), replace = FALSE)
    corr_mat[[i]] = real_cor + cor(x,mylist[[i]])
  }
  return(corr_mat)
  
}

hdilife<-perm_cor(x=hdi, y=life_exp)

map_dbl(hdilife2, median)

correlation <- as.tibble(hdilife)

props <- as.tibble(quantile(hdilife))

standard_dev <- sd(hdilife)

summary(correlation)

ggplot(correlation, aes(x=value))+geom_histogram() + labs(x= "correlation", y = "count", title = "correlation between GDP per capita and life expectency")+ geom_vline(xintercept = real_cor, col = "Blue")
```

>>>>>>> master
