<<<<<<< HEAD
---
title: "Lab 15"
author: "Data Me Pls: Chris, James, Amanda, Anna"
date: "April 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
library(tidyverse)
library(dplyr)
library(readxl)

# The Whole Data
pokemon <-read.csv(file= "pokemon.csv")

# Easier to Read Data
pokemonlite <-pokemon%>%
  select(pokedex_number, name, type1, type2, generation, is_legendary)
```

# I WANT TO BE THE VERY BEST (like no one ever was)

Our main question is how to be the best (like no one ever was). Like the famous theme song says:
" I want to be the very best,
Like no one ever was. 
To catch them is my real test, #Catch Rate, Base Egg Steps
To train them is my cause! #Exp Growth

I will travel across the land, #Generation, Pokedex Number
Searching far and wide. #Type
Each Pokemon to understand #Classification, Happiness
The power that's inside! #Base Total, Against_
Pokemon! #Height, Weight
Gotta catch em' all!"

Taking data from the equally famous video game franchise, we are wondering how exactly a trainer can become the best (in the video games at least). Using the parameters set out in the original song (inclucding catch rate, type, power, happines, abilities, and much more), we seek to determine exactly what to do in order to be the very best.


#Amanda (How does gender of a pokemon correlate with the quality of it?)
```{r, eval=FALSE}


pokemon1 <- pokemon %>% select(name, pokedex_number, percentage_male, capture_rate, base_total, base_happiness) %>% mutate(gender =ifelse(percentage_male > 50, "M", ifelse(percentage_male < 50, "F", ifelse(percentage_male==50, "B", ifelse(percentage_male == NA, "N"))))) %>% na.omit

#Permutation Test
pokemonF <- pokemon1 %>% filter(gender=="F")

pokemonM <- pokemon1 %>% filter(gender=="M")

pokemonB <- pokemon1 %>% filter(gender=="B")


pokemon1 <- pokemon1$base_total
perm_mean <- function(perms = 1000, values, n1)
{
  p<-vector("double",1000)

  for (i in c(1:perms))
  {
    
    randomSamp<-sample(length(values),n1)
    randomSamp2<-vector('integer',length(values))
    g1<-values[randomSamp]
    for(j in seq(1:length(values))) 
    { 
      if (is.element(j,randomSamp)==FALSE) randomSamp2[j]<-j 
    }
  
    tf<-randomSamp2>0
    randomSamp2<-randomSamp2[tf]
    g2<-values[randomSamp2]
    
    g1_m<-mean(g1)
    g2_m<-mean(g2)
   
    d<- g1_m - g2_m
    p[i]<-d
  }
  return(p)
}
meansF <- as_tibble(perm_mean(values = pokemon1, n1 = 53))
meansM <- as_tibble(perm_mean(values = pokemon1, n1 = 149))
meansB <- as_tibble(perm_mean(values= pokemon1, n1=501)

summary(pokemonM)
summary(pokemonF)
summary(pokemonB)
summary(pokemon1)

realDiffM <- mean(pokemonM$base_total)-mean(pokemon1)
realDiffF <- mean(pokemonF$base_total)-mean(pokemon1)
realDiffB <- mean(pokemonB$base_total)-mean(pokemon1)


stdDM <- sqrt((sd(pokemonM$base_total))^2/length(pokemonM$base_total) + (sd(pokemon1))^2/length(pokemon1))
stdDF <- sqrt((sd(pokemonF$base_total))^2/length(pokemonF$base_total) + (sd(pokemon1))^2/length(pokemon1))
stdDB <- sqrt((sd(pokemonB$base_total))^2/length(pokemonB$base_total) + (sd(pokemon1))^2/length(pokemon1))

zScoreM <- realDiffM/stdDM
zScoreF <- realDiffF/stdDF
zScoreB <- realDiffB/stdDB
zScoreM
zScoreF
zScoreB

# Plots
ggplot()+geom_histogram(data=meansM, aes(x=value, fill = "lightblue", alpha=.2))+ geom_histogram(data=meansF, aes(x=value, fill = "lightpink", alpha = .2)) + geom_historgram(data=meansB, aes(x=value, fill= "lightgreen, alpha=.2")) +
  xlab("Means")+
  geom_vline(xintercept = realDiffF, color = "pink", size = .3)+ geom_vline(xintercept=realDiffM, color="blue", size = .3)+ geom_vline(xintercept=realDiffB, color= "green", size= .3)+
  ylab("Number")+
  ggtitle("Difference in Means of Base Totals Based on Gender of Pokemon")

```

#Chris

#James

#Anna (The power that's inside!)
```{r, eval=FALSE}
pokemonpwr <- pokemon%>%
  select(pokedex_number, name, hp, attack, defense, speed, sp_attack, sp_defense, base_total)
```
=======
---
title: "Lab 15"
author: "Data Me Pls: Chris, James, Amanda, Anna"
date: "April 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
library(tidyverse)
library(dplyr)
library(readxl)

# The Whole Data
pokemon <-read.csv(file= "pokemon.csv")

# Easier to Read Data
pokemonlite <-pokemon%>%
  select(pokedex_number, name, type1, type2, generation, is_legendary)
```

# I WANT TO BE THE VERY BEST (like no one ever was)

Our main question is how to be the best (like no one ever was). Like the famous theme song says:
" I want to be the very best,
Like no one ever was. 
To catch them is my real test, #Catch Rate, Base Egg Steps
To train them is my cause! #Exp Growth

I will travel across the land, #Generation, Pokedex Number
Searching far and wide. #Type
Each Pokemon to understand #Classification, Happiness
The power that's inside! #Base Total, Against_
Pokemon! #Height, Weight
Gotta catch em' all!"

Taking data from the equally famous video game franchise, we are wondering how exactly a trainer can become the best (in the video games at least). Using the paramters set out in the original song (inclucding catch rate, type, power, happines, abilities, and much more), we seek to determine exactly what to do in order to be the very best.


https://bulbapedia.bulbagarden.net/wiki/Base_stats

https://bulbapedia.bulbagarden.net/wiki/Catch_rate

https://bulbapedia.bulbagarden.net/wiki/Friendship

#Amanda 

#Chris

#James

#Anna (The power that's inside!)
```{r, eval=FALSE}
pokemonpwr <- pokemon%>%
  select(pokedex_number, name, hp, attack, defense, speed, sp_attack, sp_defense, base_total)
```

---

#Reflections on Lab 2
As a team, restate your team's goal(s) and reflect on how well you achieved it. If you could travel back in time, which is one thing you would tell your team to keep doing? Stop doing? Start doing? Discuss this as a team and add it as a section to your Final Project.

Individually, write a paragraph reflecting on: how have your six-month or 5-year goals changed? What did you learn/accomplish in this course? If you could give yourself advice at the beginning of the semester, what would you tell yourself to keep doing, stop doing, and start doing?

__Amanda:__

__Chris:__

__James:__

__Anna:__
>>>>>>> master
