---
title: "Lab 15"
author: "Data Me Pls: Chris, James, Amanda, Anna"
date: "April 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
library(tidyverse)
library(dplyr)
library(readxl)

# The Whole Data
pokemon <-read.csv(file= "pokemon.csv")

# Easier to Read Data
pokemonlite <-pokemon%>%
  select(pokedex_number, name, type1, type2, generation, is_legendary)
```

# I WANT TO BE THE VERY BEST (like no one ever was)

Our main question is how to be the best (like no one ever was). Like the famous theme song says:
" I want to be the very best,
Like no one ever was. 
To catch them is my real test, #Catch Rate, Base Egg Steps
To train them is my cause! #Exp Growth

I will travel across the land, #Generation, Pokedex Number
Searching far and wide. #Type
Each Pokemon to understand #Classification, Happiness
The power that's inside! #Base Total, Against_
Pokemon! #Height, Weight
Gotta catch em' all!"

Taking data from the equally famous video game franchise, we are wondering how exactly a trainer can become the best (in the video games at least). Using the paramters set out in the original song (inclucding catch rate, type, power, happines, abilities, and much more), we seek to determine exactly what to do in order to be the very best.


#Amanda 

#Chris

#James

#Anna (The power that's inside!)
```{r, eval=FALSE}
pokemonpwr <- pokemon%>%
  select(pokedex_number, name, hp, attack, defense, speed, sp_attack, sp_defense, base_total)
```