---
title: "Lab 11"
author: "Data Me Pls"
date: "April 2, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The Name Game

# Team stuff (James and Anna will do it this week, next week is Chris and Amanda (good luck on your matrix test))
```{r, eval=FALSE}
install.packages("babynames")
library(tidyverse)
library(babynames)
babynames<- view(babynames)
```

## Ariel and Rachel (DONE)
```{r, eval=FALSE}
babynames<- view(babynames)

fnames<- babynames%>%
  filter(sex=="F")

# Changed the years and name string ("Ra[ey]?ch")
fnamescount<- fnames%>%
  filter(year== 2017)%>%
  summarise(sum(str_detect(name, "Ar[iy]+.l") == T))

fnamestotal<- fnames%>%
  filter(year== 2017)%>%
  summarise(sum(n))
```

__Versions of Ariel and Rachel:__

Year  |Ariel    |Rachel 
------|---------|---------
1973  |3        |14
1988  |9        |22
1990  |10       |19

__Probability of Ariel and Rachel:__

Year  |Ariel     |Rachel 
------|----------|---------
1973  |3/1458168 |14/1458168
1988  |9/1780268 |22/1780268
1990  |10/1898046|19/1898046
2017  |20/1711811|7/1711811

## _The Littel_ Mermaid Effect
```{r, eval=FALSE}
ariel<- fnames%>%
  filter(str_detect(name, "Ar[iy]+.l"))%>%
  group_by(year)%>%
  summarize(sum(n))
  
asnamesp<- babynames%>%
  filter(str_detect(name, "^A"))%>%
  group_by(year)%>%
  summarise(Prop= mean(str_detect(name, "Ar[iy]+.l")))

fnamesp<- fnames%>%
  group_by(name)

ggplot()+
  geom_line(ariel, mapping=aes(x=year, y=`sum(n)`))+
  geom_vline(xintercept= 1989, col="blue")+
  geom_line(anames, mapping=aes(x=year, y=`sum(n)`))
```

TO DO:
-other names over time (prop)
-plot and describe plot

---

## Group Histogram (TO DO AT THE END)

---

## Chris

## Amanda

## James

## Anna 
```{r, eval=FALSE}
#Filtering
myname<- babynames%>%
  filter(str_detect(name, "Anna$"), sex== "F")%>%
  group_by(year)%>%
  summarize(sum(n))

myname<- myname%>%
  rename(Count= `sum(n)`, Year= year)

myname2<- babynames%>%
  filter(str_detect(name, "Anna$"), sex== "F")

anames <-babynames%>%
  filter(str_detect(name, "^Ann"), sex== "F")%>%
  group_by(year)%>%
  summarise(sum(n))

anames<- anames%>%
  rename(Count= `sum(n)`, Year= year)

#Proportion & Quantile
anamesp <-babynames%>%
  filter(str_detect(name, "^Ann"), sex== "F")%>%
  group_by(year)%>%
  summarise(Prop= mean(str_detect(name, "Anna$")))

quantile(myname2$Prop, c(0.25,0.5,0.75,1))

#ggplot
ggplot()+
  geom_line(myname, mapping=aes(x= Year, y= Count, color="Anna"))+
  geom_line(anames, mapping=aes(x= Year, y= Count, color= "'Ann'"))+
  geom_vline(xintercept= 1999, col="Green")+
  labs(title= "Popularity of Anna and 'Ann' Names", color= "Name")

```

Percentile and Proportion Section:
words words words


# What we did

__Chris:__

__Amanda:__

__James:__

__Anna:__ 